Influence of Connectivity on Dung Beetle Communities

### 2025-05-02 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
added discription of analyses and crossed off the list

### Methods: 
1. add a few sentences on drying, keys used to ID, and depositing vouchers

### Analyses
1. Write a short paragraph on how you calculated and compared species richness and diversity (hill numbers, glmm). 
1. Write a short paragraph on how you calculated and compared functional diversity (how you measured it, how you compared it)

### Results
1. answer the overview questions, them stich them together into a paragraph
 - ~~any species restricted to 1-2 habitat types~~
 - Were all species found in all blocks? Were any restricted to only 1-2 blocks?
 - Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
 - Number of species in each functional group
 - ~~most common 3-4 species~~
 - any rare species? 
 - any invasive / exotic species?

@@

>>>>

### Methods: 
1. ~~add a few sentences on drying, keys used to ID, and depositing vouchers~~

### Analyses
1. ~~Write a short paragraph on how you calculated and compared species richness and diversity (hill numbers, glmm). ~~
1. Write a short paragraph on how you calculated and compared functional diversity (how you measured it, how you compared it)

### Results
1. answer the overview questions, them stich them together into a paragraph
 - ~~any species restricted to 1-2 habitat types~~
 - ~~Were all species found in all blocks? Were any restricted to only 1-2 blocks?~~
 - Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)
 - Number of species in each functional group
 - ~~most common 3-4 species~~
 - any rare species? 
 - any invasive / exotic species?

@@

## Analysis

Biodiversity between patch types was compared using Hill numbers (Jost 2006). We looked at community composition by increasing magnitudes of diversity components (qD) of 0D (species richness), 1D (Shannon entropy), and 2D (Simpson Diversity). Diversity numbers were calculated in R studio using package hillR and modeled using package lme4. For the purposes of this project richness was modeled using a generalized linear mixed model with a poisson distribution. A qqplot of our data shows that our residuals are normally distributed (Figure 1).
